---
title: "240321_scSPOT_code_PART2"
output: html_notebook
---

Continuation of the R notebook to make it run more smoothly

```{r}
sessionInfo()
```

#### Define working directory
```{r setup}
###This need to be set to where the FCS files are
knitr::opts_knit$set(root.dir = '~/Desktop/all_fcs/renamed/')
```

#### Define the seed for the entire workflow
```{r}
#set.seed for the whole workflow, use my_seed from now on
my_seed <- 1234
set.seed(my_seed)
```

### myeloid cell re-clustering
```{r}
sce_myelo = filterSCE(sce, cluster_id %in% c("Myeloid"), k = "merging1")
rowData(sce_myelo)$marker_class = "state"
rowData(sce_myelo[c("HLA_DR","Puro", "CD11c", "CD86", "CCR7")])$marker_class = "type" 
```

```{r}
set.seed(my_seed)
sce_myelo <- cluster(sce_myelo, 
               features = "type",
               xdim = 10,
               ydim = 10,
               maxK = 30,
               verbose = FALSE, 
               seed = my_seed)   
set.seed(my_seed)
```

```{r fig.width = 8, fig.height=4}
plotExprHeatmap(sce_myelo, 
                features = "type",
                by = "cluster_id", 
                k = "meta10", 
                m = "meta10",
                scale = "first", 
                q = 0.01, 
                perc = T, 
                col_dend = F, 
                bars = T,
                row_clust = F,
                col_clust = T)
```

```{r fig.width = 16, fig.height=4}
plotExprHeatmap(sce_myelo, 
                features = "state",
                by = "cluster_id", 
                k = "meta15", 
                m = "meta10",
                scale = "first", 
                q = 0.01, 
                perc = T, 
                col_dend = F, 
                bars = T,
                row_clust = F,
                col_clust = T)
```

```{r}
set.seed(my_seed)
sce_myelo = runDR(sce_myelo, 
                  dr = "UMAP", 
                  cells = 1000, 
                  features = type_markers(sce_myelo),
                  n_neighbors = 10,
                  scale = T
                  ) 
set.seed(my_seed)
```

```{r, fig.height=6, fig.width=12}
plot_grid(ncol=3,
plotDR(sce_myelo, dr = "UMAP", color_by = "meta10"),
plotDR(sce_myelo, dr = "UMAP", color_by = "meta15"),
plotDR(sce_myelo, dr = "UMAP", color_by = "meta20")
)
```

```{r, fig.height=6, fig.width=16}
#plotting only type markers
plotDR(sce_myelo, 
       dr = "UMAP", 
       color_by = type_markers(sce_myelo),
       ncol =5,
       scale = T
       )
```

```{r, fig.height=12, fig.width=16}
plotDR(sce_myelo, 
       dr = "UMAP", 
       color_by = state_markers(sce_myelo),
       ncol =9,
       scale = T
       )
```

## Merging of clusters into specific cell types
```{r}
merging_table <- read_excel("merging_table4.xlsx")                             
merging_table 
sce_myelo <- mergeClusters(sce_myelo, k = "meta10", table = merging_table, id = "merging4", overwrite = T)
```

#### Check how your cell type decisions look on the UMAP
```{r, fig.height=4, fig.width=6}
col_order = c(brewer.pal(4,"Accent"), cols)

plot_grid(ncol = 2,
  (plotDR(sce_myelo, dr = "UMAP", color_by = "meta10")),
  (plotDR(sce_myelo, dr = "UMAP", color_by = "merging4") +  
  scale_fill_manual(values = col_order) +
  scale_color_manual(values = col_order)) 
  )
```

```{r}
p = plotDR(sce_myelo, dr = "UMAP", color_by = "merging4")

col_order = CATALYST:::.cluster_cols
pp = ggplot(p$data, aes(x, y, colour = merging4, fill = merging4)) +
  geom_point_rast(aes(x, y, colour = merging4, fill = merging4), size =0.3, alpha = 0.8) +
  scale_fill_manual(values = col_order) +
  scale_color_manual(values = col_order) +
  theme_minimal(base_size = 14) + 
  labs(y="UMAP dim2",x = "UMAP dim1") + 
  guides(fill=guide_legend(title="celltype"), colour=guide_legend(title="celltype", override.aes = list(size=5)))
  
pp
```

### save the figure 
```{r}
pdf("~/Desktop/240213_draft_figures/240214_UMAP_myelo_merging4.pdf",width=7,height=6,paper='special') 
pp
dev.off()
```



```{r}
p = plotDR(sce_myelo, dr = "UMAP", color_by = "meta10")

col_order = CATALYST:::.cluster_cols
pp = ggplot(p$data, aes(x, y, colour = meta10, fill = meta10)) +
  geom_point_rast(aes(x, y, colour = meta10, fill = meta10), size =0.3, alpha = 0.8) +
  scale_fill_manual(values = col_order) +
  scale_color_manual(values = col_order) +
  theme_minimal(base_size = 14) + 
  labs(y="UMAP dim2",x = "UMAP dim1") + 
  guides(fill=guide_legend(title="cluster#"), colour=guide_legend(title="cluster#", override.aes = list(size=5)))
  
pp
```

### save the figure 
```{r}
pdf("~/Desktop/240213_draft_figures/240214_UMAP_myelo_meta10.pdf",width=7,height=6,paper='special') 
pp
dev.off()
```


```{r}
p = plotDR(sce_myelo, dr = "UMAP", color_by = "HLA_DR")

col_order = CATALYST:::.cluster_cols
pp = ggplot(p$data, aes(x, y, colour = value, fill = value)) +
  geom_point_rast(aes(x, y, colour = value, fill = value), size =0.3, alpha = 0.8) +
  scale_fill_viridis() +
  scale_color_viridis() +
  theme_minimal(base_size = 14) + 
  labs(y="UMAP dim2",x = "UMAP dim1") + 
  guides(fill=guide_legend(title="HLA-DR"), colour=guide_legend(title="HLA-DR", override.aes = list(size=5)))
  
pp
```

### save the figure 
```{r}
pdf("~/Desktop/240213_draft_figures/240214_UMAP_myelo_HLADR.pdf",width=7,height=6,paper='special') 
pp
dev.off()
```

## plotting heatmap after clustering
```{r fig.width = 10, fig.height=6}
peh = plotExprHeatmap(sce_myelo, 
                features = "type",
                by = "cluster_id", 
                k = "merging4", 
                scale = "first", 
                q = 0.01, 
                perc = T, 
                col_dend = F,
                row_clust = F,
                bars = T)
peh
```

```{r}
pdf("~/Desktop/240213_draft_figures/240214_UMAP_myelo_merging4_heat.pdf",width=5.7,height=1.7,paper='special') 
peh
dev.off()
```

#### Add the info about cell types to the metadata
```{r}
df = as.data.frame(sce_myelo@colData$cluster_id)
lookup = sce_myelo@metadata$cluster_codes
new <- df  # create a copy of df

# using lapply, loop over columns and match values to the look up table. store in "new".
new[] <- lapply(df, function(x) lookup$merging4[match(x, lookup$som100)])
sce_myelo$merging4 = new$`sce_myelo@colData$cluster_id`
```

# replace subsets by merging4
```{r}
sce_myelo$subsets = sce_myelo$merging4
```

```{r}
p = plotDR(sce_myelo, dr = "UMAP", color_by = "subsets", facet_by = "subsets")
p + stat_density_2d(geom = "polygon", contour = TRUE,
                  aes(fill = after_stat(level)), colour = "black",
                  bins = 5) +
  scale_fill_distiller(palette = "Spectral", direction = -1) +
  theme_classic()
```
```{r}
p = plotDR(sce_myelo, dr = "UMAP", color_by = "subsets")
p + stat_density_2d(geom = "polygon", contour = TRUE,
                  aes(fill = after_stat(level)), colour = "black",
                  bins = 5) +
  scale_fill_distiller(palette = "Spectral", direction = -1) +
  theme_classic()
p
```

## make subset column for NK cells
```{r}
sce_NK = filterSCE(sce, cluster_id %in% c("NK cells"), k = "merging1")
sce_NK$subsets = "NK"
```

## B cell re-clustering
```{r}
sce_B = filterSCE(sce, cluster_id %in% c("B cells"), k = "merging1")
rowData(sce_B)$marker_class = "state"
rowData(sce_B[c("IgD", "CD27", "CD38", "CD11c", "Tbet", "CD98", "CD39", "CytC", "CXCR5", "CCR6", "CCR7")])$marker_class = "type"
```

```{r}
set.seed(my_seed)
sce_B <- cluster(sce_B, 
               features = "type",
               xdim = 10,
               ydim = 10,
               maxK = 30,
               verbose = FALSE, 
               seed = my_seed)   
set.seed(my_seed)
```

```{r fig.width = 8, fig.height=4}
plotExprHeatmap(sce_B, 
                features = "type",
                by = "cluster_id", 
                k = "meta10", 
                m = "meta10",
                scale = "first", 
                q = 0.01, 
                perc = T, 
                col_dend = F, 
                bars = T,
                row_clust = F,
                col_clust = T)
```

```{r fig.width = 10, fig.height=4}
plotExprHeatmap(sce_B, 
                features = "state",
                by = "cluster_id", 
                k = "meta10", 
                m = "meta10",
                scale = "first", 
                q = 0.01, 
                perc = T, 
                col_dend = F, 
                bars = T,
                row_clust = F,
                col_clust = T)
```

```{r}
set.seed(my_seed)
sce_B = runDR(sce_B, 
                  dr = "UMAP", 
                  cells = 1000, 
                  features = type_markers(sce_B),
                  n_neighbors = 10,
                  scale = T
                  ) 
set.seed(my_seed)
```

```{r, fig.height=8, fig.width=18}
plot_grid(ncol=3,
plotDR(sce_B, dr = "UMAP", color_by = "meta10"),
plotDR(sce_B, dr = "UMAP", color_by = "meta15"),
plotDR(sce_B, dr = "UMAP", color_by = "meta20")
)
```

```{r, fig.height=8, fig.width=16}
#plotting only type markers
plotDR(sce_B, 
       dr = "UMAP", 
       color_by = type_markers(sce_B),
       ncol =5
       )
```

```{r}
plotDR(sce_B, dr = "UMAP", color_by = "meta10")
```

```{r, fig.height=12, fig.width=16}
#plotting only state markers
plotDR(sce_B, 
       dr = "UMAP", 
       color_by = state_markers(sce_B),
       ncol =8
       )
```

## Merging of clusters into specific cell types
```{r}
merging_table <- read_excel("merging_table6.xlsx")                             
merging_table 
sce_B <- mergeClusters(sce_B, k = "meta10", table = merging_table, id = "merging6", overwrite = T)
```

#### Check how your cell type decisions look on the UMAP
```{r, fig.height=8, fig.width=12}
col_order = c(brewer.pal(4,"Accent"), cols)

plot_grid(ncol = 2,
  (plotDR(sce_B, dr = "UMAP", color_by = "meta10")),
  (plotDR(sce_B, dr = "UMAP", color_by = "merging6") +  
  scale_fill_manual(values = col_order) +
  scale_color_manual(values = col_order)) 
  )
```

#### Add the info about cell types to the metadata
```{r}
df = as.data.frame(sce_B@colData$cluster_id)
lookup = sce_B@metadata$cluster_codes
new <- df  # create a copy of df

# using lapply, loop over columns and match values to the look up table. store in "new".
new[] <- lapply(df, function(x) lookup$merging6[match(x, lookup$som100)])
sce_B$merging6 = new$`sce_B@colData$cluster_id`
```

# replace subsets by merging6
```{r}
sce_B$subsets = sce_B$merging6
```

```{r}
p = plotDR(sce_B, dr = "UMAP", color_by = "subsets", facet_by = "subsets")
p + stat_density_2d(geom = "polygon", contour = TRUE,
                  aes(fill = after_stat(level)), colour = "black",
                  bins = 5) +
  scale_fill_distiller(palette = "Spectral", direction = -1) +
  theme_classic()
```
```{r}
p = plotDR(sce_B, dr = "UMAP", color_by = "subsets")
p + stat_density_2d(geom = "polygon", contour = TRUE,
                  aes(fill = after_stat(level)), colour = "black",
                  bins = 5) +
  scale_fill_distiller(palette = "Spectral", direction = -1) +
  theme_classic()
p
```

```{r}
p = plotDR(sce_B, dr = "UMAP", color_by = "merging6")

col_order = CATALYST:::.cluster_cols
pp = ggplot(p$data, aes(x, y, colour = merging6, fill = merging6)) +
  geom_point_rast(aes(x, y, colour = merging6, fill = merging6), size =0.3, alpha = 0.8) +
  scale_fill_manual(values = col_order) +
  scale_color_manual(values = col_order) +
  theme_minimal(base_size = 14) + 
  labs(y="UMAP dim2",x = "UMAP dim1") + 
  guides(fill=guide_legend(title="celltype"), colour=guide_legend(title="celltype", override.aes = list(size=5)))
  
pp
```

### save the figure 
```{r}
pdf("~/Desktop/240213_draft_figures/240214_UMAP_B_merging6.pdf",width=7,height=6,paper='special') 
pp
dev.off()
```

```{r}
p = plotDR(sce_B, dr = "UMAP", color_by = "meta10")

col_order = CATALYST:::.cluster_cols
pp = ggplot(p$data, aes(x, y, colour = meta10, fill = meta10)) +
  geom_point_rast(aes(x, y, colour = meta10, fill = meta10), size =0.3, alpha = 0.8) +
  scale_fill_manual(values = col_order) +
  scale_color_manual(values = col_order) +
  theme_minimal(base_size = 14) + 
  labs(y="UMAP dim2",x = "UMAP dim1") + 
  guides(fill=guide_legend(title="cluster#"), colour=guide_legend(title="cluster#", override.aes = list(size=5)))
  
pp
```

### save the figure 
```{r}
pdf("~/Desktop/240213_draft_figures/240214_UMAP_B_meta10.pdf",width=7,height=6,paper='special') 
pp
dev.off()
```

## plotting heatmap after clustering
```{r fig.width = 10, fig.height=6}
peh = plotExprHeatmap(sce_B, 
                features = "type",
                by = "cluster_id", 
                k = "merging6", 
                scale = "first", 
                q = 0.01, 
                perc = T, 
                col_dend = F,
                row_clust = F,
                bars = T)
peh
```

```{r}
pdf("~/Desktop/240213_draft_figures/240214_UMAP_B_merging6_heat.pdf",width=6,height=1.7,paper='special') 
peh
dev.off()
```

### make subset column for metab_lo cells
```{r}
sce_metab_lo = filterSCE(sce, cluster_id %in% c("metab_lo"), k = "merging1")
sce_metab_lo$subsets = "metab_lo"
```

# make an annotated combined sce of all subsets
Now we are combining all sce's again to make the downstream plotting easier
```{r}
#have to reset marker classes before combining
rowData(sce_CD4)$marker_class = "state"
rowData(sce_CD8)$marker_class = "state"
rowData(sce_myelo)$marker_class = "state"
rowData(sce_B)$marker_class = "state"
rowData(sce_NK)$marker_class = "state"
rowData(sce_enTreg)$marker_class = "state"
rowData(sce_Tfr)$marker_class = "state"
rowData(sce_metab_lo)$marker_class = "state"

rowData(sce_CD4)$used_for_clustering = "FALSE"
rowData(sce_CD8)$used_for_clustering = "FALSE"
rowData(sce_myelo)$used_for_clustering = "FALSE"
rowData(sce_B)$used_for_clustering = "FALSE"
rowData(sce_NK)$used_for_clustering = "FALSE"
rowData(sce_enTreg)$used_for_clustering = "FALSE"
rowData(sce_Tfr)$used_for_clustering = "FALSE"
rowData(sce_metab_lo)$used_for_clustering = "FALSE"
```

```{r}
sce_CD4_clean = sce_CD4 #backup not to overwrite original
colData(sce_CD4_clean) = colData(sce_CD4)[c(1:3,7)]

sce_CD8_clean = sce_CD8 #backup not to overwrite original
colData(sce_CD8_clean) = colData(sce_CD8)[c(1:3,7)]

sce_myelo_clean = sce_myelo #backup not to overwrite original
colData(sce_myelo_clean) = colData(sce_myelo)[c(1:3,length(colData(sce_myelo)))]

sce_B_clean = sce_B #backup not to overwrite original
colData(sce_B_clean) = colData(sce_B)[c(1:3,length(colData(sce_B)))]

sce_NK_clean = sce_NK #backup not to overwrite original
colData(sce_NK_clean) = colData(sce_NK)[c(1:3,length(colData(sce_NK)))]

sce_enTreg_clean = sce_enTreg #backup not to overwrite original
colData(sce_enTreg_clean) = colData(sce_enTreg)[c(1:3,length(colData(sce_enTreg)))]

sce_Tfr$subsets = "Tfr"
sce_Tfr_clean = sce_Tfr #backup not to overwrite original
colData(sce_Tfr_clean) = colData(sce_Tfr)[c(1:3,length(colData(sce_Tfr)))]

sce_metab_lo_clean = sce_metab_lo #backup not to overwrite original
colData(sce_metab_lo_clean) = colData(sce_metab_lo)[c(1:3,length(colData(sce_metab_lo)))]
```

```{r}
#then combine the dataset like this:
sce_recombined = cbind(sce_CD4_clean, sce_CD8_clean, sce_myelo_clean, sce_B_clean, sce_NK_clean, sce_enTreg_clean,sce_Tfr_clean,sce_metab_lo_clean, deparse.level=1)
```

```{r}
#export the annotated
saveRDS(sce_recombined,"231102_sce_recombined_scSPOT_summary.rds")
```
