---
title: "240321_scSPOT_code_PART3"
output: html_notebook
---

#### Load required packages
```{r}
# load required packages
library(readxl)
library(cowplot)
library(CATALYST)
library(diffcyt)
library(ggplot2)
library(flowCore)
library(reshape)
library(ggrepel)
library(premessa)
library(flowCore)
library(plyr)
library(ggpubr)
library(dplyr)
library(stringr)
library(RColorBrewer)
library(ggrastr)
library(viridis)
library(MoMAColors)
```

```{r}
sessionInfo()
```

#### re-load the recombined sce
```{r}
sce_recombined = readRDS("~/Desktop/231102_sce_recombined_scSPOT_summary.rds")
```

#### Define the seed for the entire workflow
```{r}
#set.seed for the whole workflow, use my_seed from now on
my_seed <- 1234
set.seed(my_seed)
```

#### cluster_id needs to be present for filterSCE (even though it's not used)
```{r}
sce_recombined$cluster_id = 1
```

## 240229 Calculate percentage of Treg subsets in nTreg culture
```{r}
sce_oi = filterSCE(sce_recombined, condition %in% c("stim_10x_nTreg"))
sce_oi = filterSCE(sce_oi, subsets %in% c("eTreg", "nTreg", "Tfr"))
sce_oi = filterSCE(sce_oi, !(patient_id %in% c("T00_D1","T01_D1","T02_D1","T02_D2","T03_D1","T03_D3")))
table(sce_oi$condition, sce_oi$patient_id)
```

```{r}
pc = plotCounts(sce_oi, 
    prop = TRUE,
    group_by = "patient_id", 
    color_by = "subsets")
pc
```

```{r}
cols = c(brewer.pal(9,"Reds")[c(7)], brewer.pal(9,"Purples")[c(7)],brewer.pal(9,"Blues")[c(7)])

datas = pc$data

datas$subsets = factor(datas$subsets, levels = c("nTreg", "Tfr", "eTreg"))

g = ggplot(data = datas,
        aes(y = value*100, x = subsets)) +
        geom_boxplot(width = 0.8, guides = FALSE, outlier.size = 0, alpha = 1, color = "black") +
        geom_point(aes(fill = subsets, shape = patient_id), size = 2, alpha = 0.8, position = position_jitterdodge()) +
        theme_bw() +
        theme(axis.text.x=element_text(angle = 90, vjust = 0.5, hjust = 1)) +
    xlab("") +
    ylab("% Treg subset in nTreg-culture") +
    theme_bw(base_size = 14) +
    scale_fill_manual(values=cols) +
    scale_color_manual(values=cols) +
  scale_shape_manual(values=c(21, 22, 23,24,25, 8, 11, 12, 13)) + expand_limits(y = 0)
g
```

```{r}
pdf(paste0("~/Desktop/240229_draft_figures/240229_percentage_Treg_subset_in_nTreg_culture.pdf"),width=3,height=2.5,paper='special') 
g
dev.off()
```

# Diffcyt 
#### Add the info about cell types to the cluster codes
Diffcyt need the cluster to be present in cluster codes. These are the original cluster codes (som100 and meta1-30)
```{r}
colnames(metadata(sce_recombined)$cluster_codes)
```

First replace the cluster_id value with the subsets name
```{r}
# how it originally looked like
sce_recombined@colData$cluster_id

# do the replacement
sce_recombined@colData$cluster_id = sce_recombined@colData$subsets

# how it looks like now
sce_recombined@colData$cluster_id
```

### edit som100 names as well
Here we are overwriting som100 with our cell subset ids. 
We need to dig deep into the data structure of the sce to do this.
N.B. for plotting etc in PART4 it is better to keep the original som100. We only do this to be able to use the diffcyt algorithm here
```{r}
# first the replacement in 3 steps
sce_recombined@metadata$cluster_codes = sce_recombined@metadata$cluster_codes[1:length(levels(sce_recombined@colData$cluster_id)),]
sce_recombined@metadata$cluster_codes[,1] = levels(sce_recombined@colData$cluster_id)
sce_recombined@metadata$cluster_codes[,1] = as.factor(sce_recombined@metadata$cluster_codes[,1])

#then check if it worked.
sce_recombined@metadata$cluster_codes
```

# remove all Tregs from the analysis
This depends on the analysis. For some comparisons they are not removed (e.g. CTLA4 blocking analysis). See the paper for details 
```{r}
sce_recombined = filterSCE(sce_recombined, !(subsets %in% c("eTreg", "nTreg", "Tfr")))
```

# remove channels that has more than one marker
```{r}
#See details about this in the paper methods
sce_recombined <- sce_recombined[-which(rownames(sce_recombined) %in% c("CD45RO_Dead")), ]
```
Note, for the Treg subsets comparisons samples are from T4-T7, and all have CD21 in "CD21_CD3". So no need to remove


## comparison 1 - 0x versus 20k eTreg
## selecting only conditions that should be compared
Before running diffcyt, the conditions that will be used for the final figures should be selected.
More or less conditions affects the significance results, because we are correcting for multiple testing.
If your final figure is e.g. only one inhibitor we should exclude all others at this stage.
```{r}
sce_oi = filterSCE(sce_recombined, condition %in% c("stim_0x_Treg", "stim_10x_eTreg", "stim_10x_nTreg", "stim_10x_Tfr"))
```

```{r}
# make a table, to see which of the replicates has all conditions being compared. And subset to these replicates
table(sce_oi$patient_id, sce_oi$condition)
```

```{r}
sce_oi = filterSCE(sce_oi, !(patient_id %in% c("T00_D1","T01_D1","T02_D1","T02_D2","T03_D1","T03_D3")))
```

```{r}
# check again that we filtered correctly
table(sce_oi$patient_id, sce_oi$condition)
```

Even though diffcyt statistics depends on all input conditions, it is only possible to do pairwise comparisons (i.e. two conditions at the same time). 

```{r}
# get the metadata from the "experiment info - ei"
md <- ei(sce_oi)

# define the base condition to compare to. E.g. a condition without any Tregs
md$condition <- relevel(md$condition, ref = "stim_0x_Treg")

# create a design matrix. Here we want to compare conditions, but taking into account patient differences 
design <- createDesignMatrix(md, cols_design = c("condition", "patient_id"))

# contrast is where you select the condition to compare the base condition to
# it is easier to adjust the number of contrast using the error message you get if it is incorrect
# it is also easier to place the 1 correctly after seeing the below data frame
# so just keep running this chunk till it is correct
contrast <- createContrast(c(0,1,0,0,0,0,0,0,0,0,0,0))
data.frame(parameters = colnames(design), contrast)
```

## run the diffcyt algorithm
```{r}
# DA comparisons are always the cell type. 
# we have to select som100 as the clustering to use because we added the cell type info to this column of the cluster codes
# usually for DA we use the edgeR statistics, but there are other options

res_DA <- diffcyt(sce_oi,
                  clustering_to_use = "som100",
                  analysis_type = "DA", 
                  method_DA = "diffcyt-DA-edgeR",
                  design = design, 
                  contrast = contrast,
                  verbose = TRUE)

# DS analysis is all the markers on all the cells
# also here we have to chose som100
# Instead of edgeR we use limma statistics, but there are other options
# diffcyt standard code is to test only the state markers. To overrule this, edit the markers to test. 

res_DS <- diffcyt(sce_oi,
                  clustering_to_use = "som100",
                  analysis_type = "DS", 
                  method_DS = "diffcyt-DS-limma",
                  design = design, 
                  contrast = contrast,
                  markers_to_test = T, #Note! This will include all markers instead of just state markers!
                  verbose = TRUE)

# afterwards make tables of the results
tbl_DA1 <- rowData(res_DA$res)
tbl_DS1 <- rowData(res_DS$res)
```

#### Plot a Heatmap of the DA results
```{r fig.width = 10}
# again we have to select som100.
# all is used to select all cell types instead of only significant ones
plotDiffHeatmap(sce_oi, 
                tbl_DA1,
                k = "som100",
                all = TRUE, #logical specifying whether all top_n results should be displayed. If TRUE, fdr,lfc filtering is skipped.
                sort_by = "lfc",
                assay = "exprs",
                fun = "median",
                normalize = T,
                col_anno = T, 
                row_anno = T, 
                lfc_pal = c("Navy", "white", "red"), 
                fdr_pal = c("lightgrey", "gold")
                )
```

#### Plot a Volcano plot of the DA results
I find it easier to overview the results from a volcano plot. 
Below is ggplot code to make a volcano plot of the results.
```{r, fig.height=5,fig.width=8}
vp = as.data.frame(tbl_DA1)

# to give colours dependent on significance we first subset a bit based on desired cutoffs 
# it is recommended to use the adjusted p value (adjusted for multiple testing, p_adj). 
vp_sign_up = subset(vp, logFC>0 & p_adj<0.05)
vp_sign_dn = subset(vp, logFC<0 & p_adj<0.05)
vp_non_sign = subset(vp, p_adj>0.05 )
vp_name1 = subset(vp, p_adj<0.05)
vp_name2 = subset(vp, abs(logFC)>0.3 & p_adj>0.05)

# the plot is first made with three similar pieces of code to differentally colour the non-significant, the up-regulated, and the downregulated cell types
# afterwards we add text identifiers to cells also selected by cutoff above.

vp_plot1= ggplot() +
  geom_point(
      data = vp_non_sign,
      aes(x = logFC, y = -log10(p_adj),size = logCPM),
      alpha = 0.2,
      fill = "grey",
      color = "black",
      pch = 21
    ) +
  geom_point(
      data = vp_sign_up,
      aes(x = logFC, -log10(p_adj), size = logCPM),
      alpha = 0.8,
      fill = brewer.pal(9,"Blues")[7],
      color = "black",
      pch = 21
    ) +
    geom_point(
      data = vp_sign_dn,
      aes(x = logFC, -log10(p_adj), size = logCPM),
      alpha = 0.8,
      fill = brewer.pal(9,"Blues")[5],
      color = "black",
      pch = 21
    ) +
  geom_text_repel(
      data = vp_name1,
      aes(x = logFC, -log10(p_adj), label=cluster_id),
      size = 5.5,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 100
        ) +
    geom_text_repel(
      data = vp_name2,
      aes(x = logFC, -log10(p_adj), label=cluster_id),
      size = 4,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 100
        ) +
    theme_bw(base_size = 14) +
    labs(size="", x = "logFC", y = "-log10(p_adj)") +
    guides(size=guide_legend(override.aes=list(fill="white"))) +
    ggtitle("no Treg                                   eTreg") +     geom_vline(xintercept=0, linetype='dotted', col = 'black')

vp_plot1
```

```{r}
pdf("~/Desktop/240226_draft_figures/240226_eTreg_Cell_volcano.pdf",width=5.33,height=4,paper='special') 
vp_plot1
dev.off()
```


#### Plot a Heatmap of the DS results
DS plots are similar to DA, except now we are plotting the markers
```{r fig.width = 10}
plotDiffHeatmap(sce_oi, 
                tbl_DS1,
                k = "som100",
                fdr = 0.1, 
                all = T, #logical specifying whether all top_n results should be displayed. If TRUE, fdr,lfc filtering is skipped.
                sort_by = "lfc",
                assay = "exprs",
                fun = "median",
                normalize = T,
                col_anno = T, 
                row_anno = T, 
                lfc_pal = c("Navy", "white", "red"), 
                fdr_pal = c("lightgrey", "gold")
                )
```

#### Plot a Volcano plot of the DS results
```{r, fig.height=5,fig.width=8}
vp = as.data.frame(tbl_DS1)

# zero expression may result in NAs which we remove
vp = na.omit(vp)

# the name will be a combination of the cell type and the marker
vp$name =  paste("(",vp$cluster_id,"_",vp$marker_id,")")
vp$name = gsub(" ", "", vp$name, fixed = TRUE)

# here the code is similar to DA plots
vp_sign_up = subset(vp, logFC>log(1.25,2) & p_adj<0.05 | logFC>0.33 & p_adj<0.05)
vp_sign_dn = subset(vp, logFC<(-log(1.25,2)) & p_adj<0.05 | logFC<(-0.33) & p_adj<0.05)
vp_non_sign = subset(vp, p_adj>0.05 | abs(logFC)<log(1.25,2))
vp_name = subset(vp, abs(logFC)>log(1.25,2) & p_adj<0.05 | abs(logFC)>0.33 & p_adj<0.05)


vp_plot2= ggplot() +
  geom_point(
      data = vp_non_sign,
      aes(x = logFC, y = -log10(p_adj),size = AveExpr),
      alpha = 0.2,
      fill = "grey",
      color = "black",
      pch = 21
    ) +
  geom_point(
      data = vp_sign_up,
      aes(x = logFC, -log10(p_adj), size = AveExpr),
      alpha = 0.8,
      fill = brewer.pal(9,"Blues")[7],
      color = "black",
      pch = 21
    ) +
    geom_point(
      data = vp_sign_dn,
      aes(x = logFC, -log10(p_adj), size = AveExpr),
      alpha = 0.8,
      fill = brewer.pal(9,"Blues")[5],
      color = "black",
      pch = 21
    ) +
  geom_text_repel(
      data = vp_name,
      aes(x = logFC, -log10(p_adj), label=name),
      size = 3,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 100
        ) +
    theme_bw(base_size = 14) +
    labs(size="", x = "logFC", y = "-log10(p_adj)") +
    guides(size=guide_legend(override.aes=list(fill="white"))) +
    ggtitle("no Treg                                                 eTreg") +     geom_vline(xintercept=0, linetype='dotted', col = 'black')

vp_plot2
```

```{r}
pdf("~/Desktop/240314_draft_figures/240315_eTreg_Markers_volcano.pdf",width=6,height=4.5,paper='special') 
vp_plot2
dev.off()
```

## comparison 2 - 0x versus 20k nTreg
```{r}
# get the metadata from the "experiment info - ei"
md <- ei(sce_oi)

# define the base condition to compare to. E.g. DMSO
md$condition <- relevel(md$condition, ref = "stim_0x_Treg")

# create a design matrix. Here we want to compare conditions, but taking into account patient differences 
design <- createDesignMatrix(md, cols_design = c("condition", "patient_id"))

# contrast is where you select the condition to compare the base condition to
contrast <- createContrast(c(0,0,1,0,0,0,0,0,0,0,0,0))
data.frame(parameters = colnames(design), contrast)
```

## run the diffcyt algorithm
```{r}
res_DA <- diffcyt(sce_oi,
                  clustering_to_use = "som100",
                  analysis_type = "DA", 
                  method_DA = "diffcyt-DA-edgeR",
                  design = design, 
                  contrast = contrast,
                  verbose = TRUE)

res_DS <- diffcyt(sce_oi,
                  clustering_to_use = "som100",
                  analysis_type = "DS", 
                  method_DS = "diffcyt-DS-limma",
                  design = design, 
                  contrast = contrast,
                  markers_to_test = T, #Note! This will include all markers instead of just state markers!
                  verbose = TRUE)

# afterwards make tables of the results
tbl_DA2 <- rowData(res_DA$res)
tbl_DS2 <- rowData(res_DS$res)
```

#### Plot a Heatmap of the DA results
```{r fig.width = 10}
plotDiffHeatmap(sce_oi, 
                tbl_DA2,
                k = "som100",
                all = TRUE, 
                sort_by = "lfc",
                assay = "exprs",
                fun = "median",
                normalize = T,
                col_anno = T, 
                row_anno = T, 
                lfc_pal = c("Navy", "white", "red"), 
                fdr_pal = c("lightgrey", "gold")
                )
```

#### Plot a Volcano plot of the DA results
```{r, fig.height=5,fig.width=8}
vp = as.data.frame(tbl_DA2)

vp_sign_up = subset(vp, logFC>0 & p_adj<0.05)
vp_sign_dn = subset(vp, logFC<0 & p_adj<0.05)
vp_non_sign = subset(vp, p_adj>0.05 )
vp_name1 = subset(vp, p_adj<0.05)
vp_name2 = subset(vp, abs(logFC)>0.3 & p_adj>0.05)

vp_plot3= ggplot() +
  geom_point(
      data = vp_non_sign,
      aes(x = logFC, y = -log10(p_adj),size = logCPM),
      alpha = 0.2,
      fill = "grey",
      color = "black",
      pch = 21
    ) +
  geom_point(
      data = vp_sign_up,
      aes(x = logFC, -log10(p_adj), size = logCPM),
      alpha = 0.8,
      fill = brewer.pal(9,"Reds")[7],
      color = "black",
      pch = 21
    ) +
    geom_point(
      data = vp_sign_dn,
      aes(x = logFC, -log10(p_adj), size = logCPM),
      alpha = 0.8,
      fill = brewer.pal(9,"Reds")[5],
      color = "black",
      pch = 21
    ) +
  geom_text_repel(
      data = vp_name1,
      aes(x = logFC, -log10(p_adj), label=cluster_id),
      size = 5.5,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 100
        ) +
    geom_text_repel(
      data = vp_name2,
      aes(x = logFC, -log10(p_adj), label=cluster_id),
      size = 4,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 100
        ) +
    theme_bw(base_size = 14) +
    labs(size="", x = "logFC", y = "-log10(p_adj)") +
    guides(size=guide_legend(override.aes=list(fill="white"))) +
    ggtitle("no Treg                 nTreg") +     geom_vline(xintercept=0, linetype='dotted', col = 'black')

vp_plot3
```

```{r}
pdf("~/Desktop/240226_draft_figures/240226_nTreg_Cell_volcano.pdf",width=5.33,height=4,paper='special') 
vp_plot3
dev.off()
```

#### Plot a Heatmap of the DS results
```{r fig.width = 10}
plotDiffHeatmap(sce_oi, 
                tbl_DS2,
                k = "som100",
                fdr = 0.1, 
                all = T, 
                sort_by = "lfc",
                assay = "exprs",
                fun = "median",
                normalize = T,
                col_anno = T, 
                row_anno = T, 
                lfc_pal = c("Navy", "white", "red"), 
                fdr_pal = c("lightgrey", "gold")
                )
```

#### Plot a Volcano plot of the DS results
```{r, fig.height=5,fig.width=8}
vp = as.data.frame(tbl_DS2)

# zero expression may result in NAs which we remove
vp = na.omit(vp)

# the name will be a combination of the cell type and the marker
vp$name =  paste("(",vp$cluster_id,"_",vp$marker_id,")")
vp$name = gsub(" ", "", vp$name, fixed = TRUE)

# here the code is similar to DA plots
vp_sign_up = subset(vp, logFC>log(1.25,2) & p_adj<0.05 | logFC>0.33 & p_adj<0.05)
vp_sign_dn = subset(vp, logFC<(-log(1.25,2)) & p_adj<0.05 | logFC<(-0.33) & p_adj<0.05)
vp_non_sign = subset(vp, p_adj>0.05 | abs(logFC)<log(1.25,2))
vp_name = subset(vp, abs(logFC)>log(1.25,2) & p_adj<0.05 | abs(logFC)>0.33 & p_adj<0.05)

vp_plot4= ggplot() +
  geom_point(
      data = vp_non_sign,
      aes(x = logFC, y = -log10(p_adj),size = AveExpr),
      alpha = 0.2,
      fill = "grey",
      color = "black",
      pch = 21
    ) +
  geom_point(
      data = vp_sign_up,
      aes(x = logFC, -log10(p_adj), size = AveExpr),
      alpha = 0.8,
      fill = brewer.pal(9,"Reds")[7],
      color = "black",
      pch = 21
    ) +
    geom_point(
      data = vp_sign_dn,
      aes(x = logFC, -log10(p_adj), size = AveExpr),
      alpha = 0.8,
      fill = brewer.pal(9,"Reds")[5],
      color = "black",
      pch = 21
    ) +
  geom_text_repel(
      data = vp_name,
      aes(x = logFC, -log10(p_adj), label=name),
      size = 3,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 100
        ) +
    theme_bw(base_size = 14) +
    labs(size="", x = "logFC", y = "-log10(p_adj)") +
    guides(size=guide_legend(override.aes=list(fill="white"))) +
    ggtitle("no Treg                                                 nTreg") +     geom_vline(xintercept=0, linetype='dotted', col = 'black')

vp_plot4
```

```{r}
pdf("~/Desktop/240226_draft_figures/240226_nTreg_Markers_volcano.pdf",width=6,height=4.5,paper='special') 
vp_plot4
dev.off()
```

## comparison 3 - 0x versus 20k Tfr
## selecting only conditions that should be compared
```{r}
# get the metadata from the "experiment info - ei"
md <- ei(sce_oi)

# define the base condition to compare to. E.g. DMSO
md$condition <- relevel(md$condition, ref = "stim_0x_Treg")

# create a design matrix. Here we want to compare conditions, but taking into account patient differences 
design <- createDesignMatrix(md, cols_design = c("condition", "patient_id"))

# so just keep running this chunk till it is correct
contrast <- createContrast(c(0,0,0,1,0,0,0,0,0,0,0,0))
data.frame(parameters = colnames(design), contrast)
```

## run the diffcyt algorithm
```{r}
res_DA <- diffcyt(sce_oi,
                  clustering_to_use = "som100",
                  analysis_type = "DA", 
                  method_DA = "diffcyt-DA-edgeR",
                  design = design, 
                  contrast = contrast,
                  verbose = TRUE)

res_DS <- diffcyt(sce_oi,
                  clustering_to_use = "som100",
                  analysis_type = "DS", 
                  method_DS = "diffcyt-DS-limma",
                  design = design, 
                  contrast = contrast,
                  markers_to_test = T, #Note! This will include all markers instead of just state markers!
                  verbose = TRUE)

# afterwards make tables of the results
tbl_DA3 <- rowData(res_DA$res)
tbl_DS3 <- rowData(res_DS$res)
```

#### Plot a Heatmap of the DA results
```{r fig.width = 10}
plotDiffHeatmap(sce_oi, 
                tbl_DA3,
                k = "som100",
                all = TRUE, #logical specifying whether all top_n results should be displayed. If TRUE, fdr,lfc filtering is skipped.
                sort_by = "lfc",
                assay = "exprs",
                fun = "median",
                normalize = T,
                col_anno = T, 
                row_anno = T, 
                lfc_pal = c("Navy", "white", "red"), 
                fdr_pal = c("lightgrey", "gold")
                )
```

#### Plot a Volcano plot of the DA results
```{r, fig.height=5,fig.width=8}
vp = as.data.frame(tbl_DA3)

vp_sign_up = subset(vp, logFC>0 & p_adj<0.05)
vp_sign_dn = subset(vp, logFC<0 & p_adj<0.05)
vp_non_sign = subset(vp, p_adj>0.05 )
vp_name1 = subset(vp, p_adj<0.05)
vp_name2 = subset(vp, abs(logFC)>0.3 & p_adj>0.05)

vp_plot5= ggplot() +
  geom_point(
      data = vp_non_sign,
      aes(x = logFC, y = -log10(p_adj),size = logCPM),
      alpha = 0.2,
      fill = "grey",
      color = "black",
      pch = 21
    ) +
  geom_point(
      data = vp_sign_up,
      aes(x = logFC, -log10(p_adj), size = logCPM),
      alpha = 0.8,
      fill = brewer.pal(9,"Purples")[7],
      color = "black",
      pch = 21
    ) +
    geom_point(
      data = vp_sign_dn,
      aes(x = logFC, -log10(p_adj), size = logCPM),
      alpha = 0.8,
      fill = brewer.pal(9,"Purples")[5],
      color = "black",
      pch = 21
    ) +
      geom_text_repel(
      data = vp_name1,
      aes(x = logFC, -log10(p_adj), label=cluster_id),
      size = 5.5,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 100
        ) +
    geom_text_repel(
      data = vp_name2,
      aes(x = logFC, -log10(p_adj), label=cluster_id),
      size = 4,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 10
        ) +
    theme_bw(base_size = 14) +
    labs(size="", x = "logFC", y = "-log10(p_adj)") +
    guides(size=guide_legend(override.aes=list(fill="white"))) +
    ggtitle("no Treg                       Tfr") +     geom_vline(xintercept=0, linetype='dotted', col = 'black')

vp_plot5
```

```{r}
pdf("~/Desktop/240226_draft_figures/240226_Tfr_Cell_volcano.pdf",width=5.33,height=4,paper='special') 
vp_plot5
dev.off()
```

#### Plot a Heatmap of the DS results
DS plots are similar to DA, except now we are plotting the markers
```{r fig.width = 10}
plotDiffHeatmap(sce_oi, 
                tbl_DS3,
                k = "som100",
                fdr = 0.1, 
                all = T, 
                sort_by = "lfc",
                assay = "exprs",
                fun = "median",
                normalize = T,
                col_anno = T, 
                row_anno = T, 
                lfc_pal = c("Navy", "white", "red"), 
                fdr_pal = c("lightgrey", "gold")
                )
```

#### Plot a Volcano plot of the DS results
```{r, fig.height=5,fig.width=8}
vp = as.data.frame(tbl_DS3)

# zero expression may result in NAs which we remove
vp = na.omit(vp)

# the name will be a combination of the cell type and the marker
vp$name =  paste("(",vp$cluster_id,"_",vp$marker_id,")")
vp$name = gsub(" ", "", vp$name, fixed = TRUE)

# here the code is similar to DA plots
vp_sign_up = subset(vp, logFC>log(1.25,2) & p_adj<0.05 | logFC>0.33 & p_adj<0.05)
vp_sign_dn = subset(vp, logFC<(-log(1.25,2)) & p_adj<0.05 | logFC<(-0.33) & p_adj<0.05)
vp_non_sign = subset(vp, p_adj>0.05 | abs(logFC)<log(1.25,2))
vp_name = subset(vp, abs(logFC)>log(1.25,2) & p_adj<0.05 | abs(logFC)>0.33 & p_adj<0.05)


vp_plot6= ggplot() +
  geom_point(
      data = vp_non_sign,
      aes(x = logFC, y = -log10(p_adj),size = AveExpr),
      alpha = 0.2,
      fill = "grey",
      color = "black",
      pch = 21
    ) +
  geom_point(
      data = vp_sign_up,
      aes(x = logFC, -log10(p_adj), size = AveExpr),
      alpha = 0.8,
      fill = brewer.pal(9,"Purples")[7],
      color = "black",
      pch = 21
    ) +
    geom_point(
      data = vp_sign_dn,
      aes(x = logFC, -log10(p_adj), size = AveExpr),
      alpha = 0.8,
      fill = brewer.pal(9,"Purples")[5],
      color = "black",
      pch = 21
    ) +
  geom_text_repel(
      data = vp_name,
      aes(x = logFC, -log10(p_adj), label=name),
      size = 3,
      min.segment.length = 0, #use to always put a line
      box.padding = unit(0.35, "lines"),
      point.padding = unit(0.3, "lines"),
      max.overlaps = 100
        ) +
    theme_bw(base_size = 14) +
    labs(size="", x = "logFC", y = "-log10(p_adj)") +
    guides(size=guide_legend(override.aes=list(fill="white"))) +
    ggtitle("no Treg                                                       Tfr") +     geom_vline(xintercept=0, linetype='dotted', col = 'black')

vp_plot6
```

```{r}
pdf("~/Desktop/240226_draft_figures/240226_Tfr_Markers_volcano.pdf",width=6,height=4.5,paper='special') 
vp_plot6
dev.off()
```

```{r}
STOP
```

There are other comparisons done in the paper, but the code is quite repetitive, so it is not included here.